### 2021-07-09 paper/paper.tex
changed to text superscript

\begin{table}
\tbl{Count of test cases from different test generation strategies.\label{tab:samplecounts}}{
\begin{tabular}{ll|lllll}
 & & Total & \multicolumn{2}{c}{$t$-way} & \multicolumn{2}{c}{Excursions} \\
Args & Vals & Combinations & Pairs & Triples & Single & Pair \\ \hline
5 & 4 & 1024 & 16 & 64 & 16 & 106 \\ \hline
5 & 8 & 32768 & 96 & 768 & 36 & 526 \\ \hline
10 & 4 & $>10^{6}$ & 28 & 143 & 31 & 436 \\ \hline
10 & 8 & $>10^{9}$ & 113 & 1223 & 71 & 2276 \\ \hline
40 & 4 & $>10^{24}$ & 45 & 290 & 121 & 7141 \\ \hline
40 & 8 & $>10^{36}$ & 166 & 2388 & 281 & 38501 \\  \hline
\end{tabular}
}
\end{table}

>>>>

\begin{table}
\tbl{Count of test cases from different test generation strategies.\label{tab:samplecounts}}{
\begin{tabular}{ll|lllll}
 & & Total & \multicolumn{2}{c}{$t$-way} & \multicolumn{2}{c}{Excursions} \\
Args & Vals & Combinations & Pairs & Triples & Single & Pair \\ \hline
5 & 4 & 1024 & 16 & 64 & 16 & 106 \\ \hline
5 & 8 & 32768 & 96 & 768 & 36 & 526 \\ \hline
10 & 4 & >10\textsuperscript{6} & 28 & 143 & 31 & 436 \\ \hline
10 & 8 & >10\textsuperscript{9} & 113 & 1223 & 71 & 2276 \\ \hline
40 & 4 & >10\textsuperscript{24} & 45 & 290 & 121 & 7141 \\ \hline
40 & 8 & >10\textsuperscript{36} & 166 & 2388 & 281 & 38501 \\  \hline
\end{tabular}
}
\end{table}
